Supplementary Information: Drought sensitivity is not a species trait: Tropical tree drought sensitivity is jointly shaped by drought characteristics, species adaptations, and individual microenvironments

### 2025-10-31 doc/manuscript_hkk_drought_sensitivity.Rmd
cosmetic edit to figure legend
small updates to code, README and statement

# Data Accessibility Statement {-}
This manuscript does not use novel code. 
The dendrometer band data used for this manuscript is archived in the ForestGEO data repository and will be made available upon request. 
The climate data used in this work are publicly available. 
The code used to analyse the data is archived in Zenodo with doi:10.5281/zenodo.15777974.

@@

***Figure `r fig_droughts`. Climatic characteristics of the focal drought years compared with the average across years*** in the Huai Kha Khaeng ForestGEO plot, for four daily climate variables: dry days, precipitation, maximum temperature and VPD.  (a) 30-day running means. (b) Anomalies of the drought year running means from the 2008-2019 averages, in units of standard deviations.  (c) Standardised Precipitation Evapotranspiration Index (SPEI) values for the drought years at four different time scales for each month for each drought year. A k-month SPEI integrates over k months ending in the current month. Across all panels, light blue background represents the average wet season, from May to October.

>>>>

# Data Accessibility Statement {-}
<!-- This manuscript does not use novel code.  -->
<!-- The dendrometer band data used for this manuscript is archived in the ForestGEO data repository and will be made available upon request.  -->
<!-- The climate data used in this work are publicly available.  -->
Data and code required to reproduce the results and figures are archived in Zenodo with doi:10.5281/zenodo.15777974.

@@

***Figure `r fig_droughts`. Climatic characteristics of the focal drought years compared with the average across years*** in the Huai Kha Khaeng ForestGEO plot, for four daily climate variables: dry days, precipitation, maximum temperature and VPD.  (a) 30-day rolling means (in colour for each year) along with their long-term mean and standard deviation (in grey). (b) Anomalies of the drought year running means from the 2008-2019 averages, in units of standard deviations. (c) Standardised Precipitation Evapotranspiration Index (SPEI) values for the drought years at four different time scales for each month for each drought year. A k-month SPEI integrates over k months ending in the current month. Across all panels, light blue background represents the average wet season, from May to October.
